\documentclass{article}

\setlength{\parindent}{0pt}

\begin{document}

% suppresses page number
\pagenumbering{gobble}

%----------BEGIN FRONT PAGE----------%
% instructions for those who know the password

\begin{center}
  \textbf{\huge Emergency Cluster Documentation}
\end{center}

\section*{\Large Shutdown}
\begin{enumerate}
\item Ensure the switcher is set to Channel 1.
\item Login as root on the CE.
  \begin{itemize}
  \item Verify logged into CE: \\{\tt\# hostname \\ uscms1.fltech-grid3.fit.edu}
  \item Verify logged in as root: \\{\tt\# whoami \\ root}
  \end{itemize}
\item Run the command: {\tt totalShutdown}
\item Once all components have been powered down, turn off the three UPSs.
\item Unplug the UPSs.
\item Unplug the two power strips behind the cluster.
\end{enumerate}

\section*{\Large Powerup}
\begin{enumerate}
\item Plug in the two power strips and the three UPSs.
\item Turn on the UPSs.
\item Set the switcher to Channel 4, and turn on the monitor.
\item Powerup NAS-0 and NAS-1.
\item Wait until a login prompt appears on the monitor to ensure that
  the NASs have fully powered up.
\item Set the switcher to Channel 1.
\item Powerup the CE and SE.
\item Wait until a login prompt appears on the monitor to ensure that
  the CE and SE have fully powered up.
\item Turn on the nodes.
\end{enumerate}

\begin{large}
If the cluster MUST be shut down, and the password is unknown, follow
the instructions on the back of this sheet.
\end{large}

\pagebreak

%-----------END FRONT PAGE-----------%

%----------BEGIN BACK PAGE----------%
% for when the cluster MUST be shutdown by those who do not know the password

\begin{center}
  \section*{Administrator Contact Information}
  \begin{tabular}{|l|r|}
    \hline
    Ryan Wojtyla & (904)613-1863 \\
    Riley Carlson & (772)214-9723 \\
    Hannah Blackburn & (919)807-9172 \\
    \hline
  \end{tabular}
\end{center}

  \subsection*{Cluster Force Shutdown}
  \begin{enumerate}
  \item
    In the right cabinet, flip all four ``Geist'' power strips to off.
  \item
    In the left cabinet, find the power button of the SE (top-right most
    button of the lowest computer) then press and hold it until all of the computer's
    lights turn off.
  \item
    In the left cabinet, find the power button of NAS-1 (bottom-left most
    button of the second lowest computer) then press and hold it until all of the
    computer's lights turn off.
  \item
    In the right cabinet, find the power button of NAS-0 (top-right
    most button of the larger of the two bottom-most computers) then press
    and hold it until all of the computer's lights turn off.
  \item
    In the right cabinet, find the power button of the CE (top-right
    most button of the smaller of the two bottom most computers) then press
    and hold it until all of the computer's lights turn off.
  \item
    In the right cabinet, find the power button of the APC UPS (labeled as ``O''
    on the machine just below NAS-0) then press and hold it until all of the
    UPS's lights turn off.
  \item
    In the right cabinet, find the power buttons of the SmartPro UPSs (the
    two machines below the APC UPS) then press and hold each of them until
    all of the UPSs' lights turn off.
  \item
    Behind the cluster, unplug the two normal plugs and the three twist-lock
    plugs. NOTE: The twist-lock plugs must first be twisted so that they may
    be unplugged.
  \end{enumerate}

%-----------END BACK PAGE-----------%

\end{document}